Pipeline Performance Figure Generation

### 2023-08-18 TestingPipeline/Scripts/paper_figure_generation.Rmd
Updates to MCC, recall, precision boxplots.

```{r}
fig <- ggplot(accuracy_scores_melt[accuracy_scores_melt$toolcombo!="0 0 1 0 0 0" & accuracy_scores_melt$performance_metric!="prop_viral",], aes(x=numrules, y=performance_metric_score, 
                                  color=numrules, fill=numrules)) +
  geom_boxplot() +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    #axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Score") +
  xlab("Number of Rule Sets") +
  scale_fill_manual(name="Number of Rule Sets",
                     values = alpha(rev(viridis(6)), 0.5)) +
  scale_color_manual(name="Number of Rule Sets",
                     values = alpha(rev(viridis(6)), 1)) +
  facet_wrap(~performance_metric) +
  geom_hline(yintercept = 0, color="grey")

@@

ggsave(
  "../IntermediaryFiles/MCC_precision_recall_boxplots.png",
  plot = fig,
  scale = 1,
  width = 8,
  height = 4,
  units = c("in", "cm", "mm", "px"),
  dpi = 300,
  limitsize = TRUE
)
```

>>>>

```{r}
fig <- ggplot(accuracy_scores_melt[accuracy_scores_melt$toolcombo!="0 0 1 0 0 0" & accuracy_scores_melt$performance_metric!="prop_viral",], aes(x=numrules, y=performance_metric_score)) +
  geom_boxplot(alpha=0.1, fill="black") +
  geom_point(alpha=0.2, fill="black", color="black") +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    #axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
    strip.background = element_rect(fill="white", color="grey"),
    strip.text = element_text(color="black", size=14)
  ) +
  ylab("Score") +
  xlab("Number of Rule Sets") +
  facet_wrap(~performance_metric) +
  geom_hline(yintercept = 0, color="grey")

@@

ggsave(
  "../IntermediaryFiles/MCC_precision_recall_boxplots_grey.png",
  plot = fig,
  scale = 1,
  width = 8,
  height = 4,
  units = c("in", "cm", "mm", "px"),
  dpi = 300,
  limitsize = TRUE
)
```
